Sun vs Shade leaves (WTCIII)

### 2015-04-02 markdown/wtc_sunshade.Rmd
new file to compare leaf N with with vcmax
final touches to markdown

removed duplciates in aci sun (need to implement this elsewhere

---
title: "Sun vs Shade leaves (WTCIII)"
author: "Court Campany"
date: "April 1, 2015"
output: html_document
---
```{r knitr_options , include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=6,
echo=FALSE, message=FALSE,
fig.align='center', warning=FALSE)
```

@@

#### <u>Design</u>
* WTCIII was a warming experiemnt with ambient and +3°C warming (n=6).  A drought manipulation was added in the last few months of the experiment.
* Sun leaves were measured in the upper canopy at their current PPFD.  Shade leaves were measured in the lower canopy, first at their current PPFD and then again at sun leaf PPFD.
* New fully expanded leaves were measured. Shade leaves were sampled into the middle canopy as the experiment progressed to avoid issues with leaf age.
* Leaf physiological measurements were taken at their current temperature (ambient, +3°C) for paired comparisons across leaf types. Thus, data below represent a large range of temperatures from ~18-35°C.
* For simplicity I have generalized most of the results below to just sun vs. shade leaves. So effects of the warming treatment are often not included and there is no standarizatiopn of leaf temperature.
* Unless it is explicitly stated I have left off the drought treatment as well.  
* Data below are mostly overall means across the 6 campaigns.  We can tease apart temperature/drought effects later.

@@

#plot
plot(sunAT_sim$Ci, sunAT_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab=cilab, ylab="", type="l", lwd=2, ylim=c(0,30))
  points(sunET_sim$Ci, sunET_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  points(shaAT_sim$Ci, shaAT_sim$ALEAF, col="yellow4", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2)
  points(shaET_sim$Ci, shaET_sim$ALEAF, col="yellow4", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  legend("bottomright", leglab2, lty=c(1,2,1,2), lwd=2,col=colaci, pt.bg=col4,inset = 0.03)
  title(ylab=satlab, mgp=ypos)
```

* ACi curves were measured at saturating light for both sun and shade leaves. 
* Here are predicted ACi curves for leaf types with temperature treatments. Both Vc<sub>max</sub> and J<sub>max</sub> are reduced in shade leaves with little effect of the temperature treatment. ACi curves were taken once towards the end of the experiment on well watered trees

@@

* The well-watered treatment from the drought treatment are seperated.  I'm more confident in the well-watered values as I was often on the cutoff point with drawdown and xsi for drought leaves. They do show similar patterns but g<sub>m</sub> seems to be higher in drought trees

* Shade leaf g<sub>m</sub> is always lower than sun leaves but when the lights are 'turned on' they have in instantaneous response in g<sub>m</sub> that resembles sun leaves.

@@

* Figures of photosynthesis and g<sub>s</sub>.  Panel (a) is shown with 95% confidence intervals.  Panel (b) shows predicted photosynthesis rates generated with g<sub>s</sub> values, mean leaf temperature and PPFD (sun/shade), and ACi parameters including ambient and elevated temperature treatments. Here we can see optimal stomatal behaviour in sun leaves but not in shade leaves.

@@

```{r,results='asis'}
##this has droughtleaves
palette(c("yellow4", "forestgreen"))
par(mar=c(5,5,2,2))
plot(c13.mean ~ leafN_area.mean, data=leaftraits, pch=16, col=as.factor(leaf), ylim=c(-35,-25), 
                 xlim=c(1,3.5), cex=1.25, xlab=narealab, ylab=c13lab)
legend("bottomright", leaflab, pch=16, col=c("yellow4", "green4"),pt.cex=1.5,inset = 0.03)

@@

* Next is the light environment in which gas exchange measurements for sun and shade leaves were measured.  This data was generated with a handheld par sensor for each individual leaf and verified with ceptometer readings within the canopy at the height of the measured leaf. There was a ~75% reduction in PPFD from sun to shave leaves.

>>>>

---
title: "Sun vs Shade leaves (WTCIII)"
author: "Court Campany"
date: "April 2, 2015"
output: html_document
---
```{r knitr_options , include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=6,
echo=FALSE, message=FALSE,
fig.align='center', warning=FALSE)
```

@@

#### <u>Design</u>
* WTCIII was a warming experiment with ambient and +3°C warming (n=6).  A drought manipulation was added in the last few months of the experiment.
* Sun leaves were measured in the upper canopy at their current PPFD.  Shade leaves were measured in the lower/middle canopy, first at their current PPFD and then again at sun leaf PPFD.
* New fully expanded leaves were measured. Shade leaves were sampled into the middle canopy as the experiment progressed to avoid issues with leaf age.
* Leaf physiological measurements were taken at their current temperature (ambient, +3°C) for paired comparisons across leaf types. Thus, data below represent a large range of temperatures from ~18-35°C.
* For simplicity I have generalized most of the results below to just sun vs. shade leaves. So effects of the warming treatment are often not included and there is no standardization of leaf temperature.
* Unless it is explicitly stated I have left off the drought treatment as well.  
* Data below are mostly overall means across the 6 campaigns.  We can tease apart temperature/drought effects later. 
* The green/brown color scheme always refers to sun leaves and shade leaves at low light

@@

* ACi curves were measured at saturating light for both sun and shade leaves.

```{r, aci plot}
#plot
plot(sunAT_sim$Ci, sunAT_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab=cilab, ylab="", type="l", lwd=2, ylim=c(0,30))
  points(sunET_sim$Ci, sunET_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  points(shaAT_sim$Ci, shaAT_sim$ALEAF, col="yellow4", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2)
  points(shaET_sim$Ci, shaET_sim$ALEAF, col="yellow4", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  legend("bottomright", leglab2, lty=c(1,2,1,2), lwd=2,col=colaci, pt.bg=col4,inset = 0.03)
  title(ylab=satlab, mgp=ypos)
```

* Here are predicted ACi curves for leaf types with temperature treatments. Both Vc<sub>max</sub> and J<sub>max</sub> are reduced in shade leaves with little effect of the temperature treatment(AT/ET). ACi curves were taken once towards the end of the experiment on well watered trees

@@

* The well-watered treatment from the drought treatment are separated.  I'm more confident in the well-watered values as I was often on the cutoff point with drawdown and thus xsi for drought leaves. They show similar patterns but g<sub>m</sub> seems to be higher in drought trees

* g<sub>m</sub> in shade is always lower than in sun but when the lights are 'turned on' shade leaves show an instantaneous response in g<sub>m</sub> that resembles sun leaves.

@@

* Figures of photosynthesis and g<sub>s</sub>.  Panel (a) is shown with 95% confidence intervals.  Panel (b) shows predicted photosynthesis rates generated with g<sub>s</sub> values, mean leaf temperature and PPFD (sun/shade), and ACi parameters including ambient and elevated temperature treatments. Here we can see optimal stomatal behavior in sun leaves but not in shade leaves.

@@

```{r,results='asis'}
##this has droughtleaves
palette(c("yellow4", "forestgreen"))
par(mar=c(5,5,2,2))
plot(c13.mean ~ leafN_area.mean, data=leaftraits, pch=16, col=as.factor(leaf), ylim=c(-35,-25), 
                 xlim=c(1,3.5), cex=1.25, xlab=narealab, ylab=c13lab)
legend("bottomright", leaflab2, pch=16, col=c("green4","yellow4"),inset = 0.03)

@@

* Here is the light environment in which gas exchange measurements for sun and shade leaves were measured.  This data was generated with a handheld par sensor for each individual leaf and verified with ceptometer readings within the canopy at the height of the measured leaf. There was a ~75% reduction in PPFD from sun to shave leaves.
